Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-03-20 paper/tex/paper.tex
update plots
test overleaf sync

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_detections_variations.pdf}
    \caption{The number of expected detections in a four year LISA mission for different DCO types and model variations. Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties. Each model is described in further detail in Table\,\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section\,\ref{sec:fiducial_physics}}
    \label{fig:model_variation_detections}
\end{figure*}

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties. The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
    \label{fig:model_variation_detections}
\end{figure*}
